Efficient toolkit implementing best practices for principal component analysis of population genetic data

### 2019-10-18 paper-bedpca.tex
save

>>>>

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Sat Oct 19 00:18:24 2019
\begin{table}[ht]
\centering
\caption{Ancestry (left) of POPRES individuals and their matching to 1000G populations (top) by our method. See the description of 1000G populations at \url{https://www.internationalgenome.org/category/population/}.} 
\label{tab:ancestry-pred-popres}
\begin{tabular}{|l|c|c|c|c|c|}
  \hline
 & EUR\_CEU & EUR\_GBR & EUR\_IBS & EUR\_TSI & NA \\ 
  \hline
Anglo-Irish Isles & 159 & 57 &  &  & 50 \\ 
  Belgium & 28 & 3 &  &  & 12 \\ 
  Central Europe & 3 &  &  & 1 & 51 \\ 
  Eastern Europe & 2 &  &  &  & 28 \\ 
  France & 14 &  & 13 &  & 62 \\ 
  Germany & 37 &  &  &  & 34 \\ 
  Italy &  &  & 12 & 19 & 188 \\ 
  Netherlands & 10 & 2 &  &  & 5 \\ 
  Scandinavia & 5 &  &  &  & 10 \\ 
  SE Europe &  &  &  & 5 & 89 \\ 
  SW Europe &  &  & 193 &  & 71 \\ 
  Switzerland & 33 & 1 & 6 &  & 182 \\ 
   \hline
\end{tabular}
\end{table}

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Sat Oct 19 00:28:24 2019
\begin{table}[ht]
\centering
\caption{Ancestry (left) of Celiac individuals and their matching to 1000G populations (top) by our method. See the description of 1000G populations at \url{https://www.internationalgenome.org/category/population/}.} 
\label{tab:ancestry-pred-celiac}
\begin{tabular}{|l|c|c|c|c|c|c|c|}
  \hline
 & AMR\_MXL & EUR\_CEU & EUR\_FIN & EUR\_GBR & EUR\_IBS & EUR\_TSI & NA \\ 
  \hline
Finland &  & 4 & 1543 & 1 &  & 1 & 922 \\ 
  Italy &  &  &  &  & 15 & 229 & 795 \\ 
  Netherlands &  & 802 &  & 382 & 1 &  & 463 \\ 
  UK & 1 & 2865 & 1 & 2532 & 4 & 5 & 1346 \\ 
   \hline
\end{tabular}
\end{table}
